---
title: "Crea tu propia lista de Warhammer 40,000"
output: html_document
date: "2024-11-18"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

Facción
```
####################################### Elije una faccion ####################################


ejercito<-function(x){
  
  faccion<<- as.numeric( readline( prompt = "Las facciones del juego son: Marines espaciales(1), Tau(2), Tiranidos(3) y Necrones(4), coloca el numero de tu faccion: \n "))           
  
  if( faccion == 1 ){
    puntos<-read.csv("Datos/Puntos de ejercito  - Marines espaciales.csv")
    print( "Has elegido a los angeles de la muerte del emperador")
    print( "Estas son las unidades disponibles: ")
    print(paste( puntos[[1]]))
    
  } else if ( faccion == 2 ){
    puntos<-read.csv("Datos/Puntos de ejercito  - Tau.csv")
    print( "Has elegido el bien mayor")
    print( "Estas son las unidades disponibles: ")
    print(paste( puntos[[1]]))
    
  } else if ( faccion == 3){
    puntos<-read.csv("Datos/Puntos de ejercito  - Tiranido.csv")
    print( "Hambreeeeeeeee")
    print( "Estas son las unidades disponibles: ")
    print(paste( puntos[[1]]))
    
  } else if ( faccion == 4){
    puntos<-read.csv("Datos/Puntos de ejercito  - Necron.csv")
    print( "¿Por qué dar un nombre a la totalidad?")
    print( "Estas son las unidades disponibles: ")
    print(paste( puntos[[1]]))
  } 
} 
ejercito()
```

document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

Tipo de Partida
When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
